---
title: "Chapter 2: Data Structures"
author: "Brynjólfur Gauti Jónsson"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Quiz

1. What are the three properties of a vector, other than its contents?

2. What are the four common types of atomic vectors? What are the two rare types?

3. What are attributes? How do you get them and set them?

4. How is a list different from an atomic vector? How is a matrix different from a data frame?

5. Can you have a list that is a matrix? Can a data frame have a column that is a matrix?

# Exercises 2.1.3

1. What are the six types of atomic vector? How does a list differ from an atomic vector?

2. What makes is.vector() and is.numeric() fundamentally different from is.list() and is.character()?

3. Test your knowledge of vector coercion rules by predicting the output of the following uses of c():

      * c(1, FALSE)
      * c("a", 1)
      * c(list(1), "a")
      * c(TRUE, 1L)
      
4. Why do you need to use unlist() to convert a list to an atomic vector? Why doesn't as.vector() work?

5. Why is 1 == "1" true? Why is -1 < FALSE true? Why is "one" < 2 false?

6. Why is the default missing value, NA, a logical vector? What's special about locial vectors? (Hint: think about c(FALSE, NA_character_).)


# Exercises 2.2.2

1. An early draft used this code to illustrate structure():

```{r}
structure(1:5, comment = "my attribute")
```

But when you print that object you don't see the comment attribute. Why? Is the attribute missing, or is there something else special about it? (Hint: try using help)

2. What happens to a factor when you modify its levels?

```{r}
f1 <- factor(letters)
levels(f1) <- rev(levels(f1))
```

3. What does this code do? How do f2 and f3 differ from f1?

```{r}
f2 <- rev(factor(letters))
f3 <- factor(letters, levels = rev(letters))
```

